### 2023-04-14 main.tex
hadamard

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
\end{equation}
Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
acting trivially as the identity on the other sites). 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
\begin{equation}\label{secondCasimir}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
More precisely,  considering the standard coproduct 
\begin{equation}
\begin{split}
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\end{split}
\end{equation}
we have 
\begin{equation}
\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}
\end{equation}
Then, one can check that 
\begin{equation}\label{hamiltonianCasimir}
	H_{x,y}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
\end{equation}
where $\Delta^{x,y}(C_2)$ denotes a copy of $\Delta(C_2)$ acting on  
the edge $(x,y)\in \mathcal{E}$.

@@

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
H_{x,y}=\sum_{a,l=1}^{N}E_{al}^{x}\otimes E_{la}^{y}-E_{ll}^{x}\otimes E_{aa}^{y}
 \end{equation}
 and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(E_{al}^{x}-E_{ll}^{x}\right)
\end{equation}
Here $E_{al}^{x}$ is a copy of $E_{al}$ defined in \eqref{actionE} acting on site $x$.

We can write this Hamiltonian in function of the coproduct of the second Casimir
\begin{equation}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
It reads
\begin{equation}
	H_{x,y}=\left\{\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}\right\}
\end{equation}
Here we introduced the standard coproduct
\begin{equation}
\begin{split}
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\end{split}
\end{equation} acting on sites $x,y$ and used that $C_{2}|n\rangle=\twoj(\twoj+N)|n\rangle$. 
\end{comment}

@@

    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}H_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 

@@

    H_{x,y}^{T}D=DH_{x,y}\qquad \forall (x,y)\in \mathcal{E}

@@

\paragraph{Proof of \eqref{edgeDualRealtion}.}To show this relation we need two 'ingredients'. First the existence of a similarity transformation between the Hamiltonian $H_{x,y}$  and its transposed. As we will show, this similarity transformation is $R_{x}R_{y}$.  Second, the possibility of finding a symmetry for the edge Hamiltonian. Exploiting \eqref{hamiltonianCasimir}, we will search for a symmetry of the second Casimir $C_{2}$. As we will see, this symmetry is $\sum_{a=2}^{N}E_{a1}$ \\
We first look for the similarity between $H_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain

\begin{equation}\label{transpositionPropertyH}
    H_{x,y}^{T}=\left(R_{x}R_{y}\right)H_{x,y}\left(R_{x}R_{y}\right)^{-1}
\end{equation}
therefore we have found the similarity transformation between $H_{x,y}$ and its transposed. \\
We now look for a symmetry of $H_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
\begin{equation}
	H_{x,y}S_{x,y}=S_{s,y}H_{x,y}\quad \Leftrightarrow \quad [H_{x,y},S_{x,y}]=0
\end{equation}
Using \eqref{hamiltonianCasimir}, we observe that $H_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term. Therefore, it is enough to look for a symmetry of $\Delta (C_{2})$. Using the bilinearity of the coproduct operator and the fact that $C_{2}$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$ it holds
\begin{equation}
	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2}),\Delta(E)) \right]=0
\end{equation}
We chose 
\begin{equation}
	E=\sum_{a=2}^{N}E_{a1}
\end{equation}
and, for a fixed $(x,y)\in \mathcal{E}$, we define
\begin{equation}
	S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. Therefore, this operator $S_{x,y}$ satisfies
\begin{equation}\label{symmetryH}
	\left[S_{x,y},H_{x,y}\right]=0
\end{equation}
i.e. it is a symmetry of $H_{x,y}$. \\ Exploiting these considerations we write

\begin{comment}
As already pointed out, $H_{x,y}$ is a linear function of $\Delta(C_{2})$. This implies that symmetries of  $\Delta(C_{2})$ are also symmetries of  $H_{x,y}$. Moreover, the coproduct is a Lie algebra homomorphism, i.e. $\forall A,B\in gl(N)$
\begin{equation}\label{symmetryCoproduct}
    [A,B]=0\quad \Longrightarrow\quad \left[\Delta(A),\Delta(B)\right]=0
\end{equation}
This tells us that it is enough to find a symmetry of $C_{2}$. This element belongs to the center of $gl(N)$, and therefore it commutes with all the element of this algebra. Consider
\begin{equation}\label{equationE}
    E=\sum_{a=2}^{N}E_{a1}
\end{equation}
To obtain a product structure of the elements of the duality matrix, we introduce
\begin{equation}
    S=\exp{(\Delta(E))}
\end{equation}
Finally, for fixed $(x,y)\in \mathcal{E}$, we define
\begin{equation}
    S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. This operator $S^{x,y}$ satisfies
\begin{equation}\label{symmetryH}
    \left[S_{x,y},H_{x,y}\right]=0
\end{equation}
i.e. $S_{x,y}$ is a symmetry of $H_{x,y}$. \\ Exploiting these considerations we write
\end{comment}
\begin{equation}
    \begin{split}
        H_{x,y}^{T}D&=(R_{x}R_{y})H_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)H_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=
        DH_{x,y}
    \end{split}
\end{equation}
 where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
 %\textbf{Reamrk}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $a\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
 %{\color{blue} That's confusing. What is E?}

@@

@@

	H=B_{1}+H_{bulk}+B_{L}

@@

	B_{1}=\begin{pmatrix}

@@

	B_{L}=\begin{pmatrix}

@@

reduces to the identity which implies $e_{ab}^T= e_{ba}$. Therefore, the duality matrix reads

@@

	\widetilde{H}=\widetilde{H}_{0}+\sum_{x=1}^{L-1}H_{x,x+1}+\widetilde{H}_{L+1}

@@

@@

	H\;\xrightarrow{\mathcal{S}_{1}}\;H^{'}\;\xrightarrow{\mathcal{S}_{2}}\;H^{''}
where $H^{'}= \mathcal{S}_{1} H \mathcal{S}_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = \mathcal{S}_{2}H' \mathcal{S}_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly. Then, reversing the transformations we will retrieve $|\Psi\rangle$.

The first transformation $\mathcal{S}_{1}$ is closely related to the dual matrix. Moreover, we will see that $H^{'}$ is $\widetilde{H}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $\mathcal{S}_{2}$ diagonalize the right boundary. The composition  $\mathcal{S}_{2} \mathcal{S}_{1}$ allows to simplify the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs.

The computation are organized as follows: we first define the similarity transformations $\mathcal{S}_{1},\mathcal{S}_{2}$ and the Hamiltonians $H^{'},H^{''}$. Second, we compute the steady state of $H^{''}$ thanks to the simpler commutators. Finally, we invert the similarities and retrieve the steady state of $H^{'}$ and $H$ respectively.

\begin{comment}
{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA gives the steady state in terms of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
\end{comment}
\subsubsection{The similarity transformations}\label{subsectionSTransf}
We introduce the first transformation as
\begin{equation}\label{transformationV}
 S_{1}:=\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
\end{equation}
Observe that $S_{1}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}). By taking the tensor product over the chain we define
\begin{equation}
    \mathcal{S}_{1}=S_{1}^{\otimes L}
\end{equation}
that is related with the duality matrix by 
\begin{equation}
\mathcal{S}_{1}=\prod_{x=1}^{L}d_{x}^{T}
\end{equation}
 This $\mathcal{S}_{1}$ is invertible, then we introduce 
\begin{equation}\label{hatHamiltonian}
   H^{'}:=B^{'}_{1}+H_{bulk}+B^{'}_{L}
\end{equation}
that is related to $H$ by
\begin{equation}\label{similarV}
   H=\mathcal{S}_{1}^{-1}H^{'}\mathcal{S}_{1}
\end{equation}
The boundary Hamiltonians $B_{1}^{'}$ and $B_{L}^{'}$ relates to the transposed of  $\widetilde{H}_{0}$ and $\widetilde{H}_{L+1}$, the boundary part of the dual Hamiltonian  defined in \eqref{siteDualHamiltonian},
they are obtained replacing the  extra-site bosonic creation operators $(a^{\dagger})_{a}^{0}$  (resp. $(a^{\dagger})_{a}^{L+1}$) with the corresponding reservoir parameters $\alpha_a$ (resp. $\beta_a$):
\begin{equation}
	B^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\qquad B^{'}_{L}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
\end{equation}
Obviously
\begin{equation}\label{S1-Inverse}
	|\Psi\rangle =\mathcal{S}_{1}^{-1}|\Psi^{'}\rangle
\end{equation}
where $|\Psi^{'}\rangle$ satisfies $H^{'}|\Psi^{'}\rangle=0$.

>>>>

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
\mathcal{H}_{x,y}=\sum_{a,b=1}^{N}\Big(E_{ab}^{x} E_{b a}^{y}-E_{bb}^{x} E_{aa}^{y}\Big)
 \end{equation}
  and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,b=1}^{N}\alpha_{a}^{x}\left(E_{ab}^{x}-E_{bb}^{x}\right)
\end{equation}
Here $E_{ab}^{x}$ is a copy of $E_{ab}$ defined in \eqref{actionE} acting on site $x$ (and
acting trivially as the identity on the other sites). 
Following  \cite{belitsky2015self}, the Hamiltonian and the genertor are linked by
\begin{equation}\label{Hamiltonian-Generator}
H=\mathcal{L}^{T}
\end{equation}
The action of the generator can also be expressed as 
\begin{equation}
    \mathcal{L}f( {\bf n})=\langle f|H| {\bf n}\rangle
\end{equation}
where 
\begin{equation}
    \langle f|=\sum_{ {{\bf n}\in \Omega}}f( {\bf n})\langle  {\bf n}|
\end{equation}

We can write the edge Hamiltonian \eqref{edgeHamiltonian} as a function of the coproduct of the second Casimir of $gl(N)$
\begin{equation}\label{secondCasimir}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
that acts diagonally as $C_{2}|\mathbf{n}\rangle=\twoj(\twoj+N)|\mathbf{n}\rangle$ and belogs to the center of $gl(N)$ (i.e. it commutes with all the algebra elements).  
More precisely,  considering the standard coproduct 
\begin{equation}
\begin{split}
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\end{split}
\end{equation}
we have 
\begin{equation}
\Delta(C_{2})=\sum_{a,b=1}^{N}\Delta(E_{ab})\Delta(E_{ba})=2\sum_{a,b=1}^{N}E_{ab}\otimes E_{ba}+C_{2}\otimes \mathbbm{1}+\mathbbm{1}\otimes C_{2}
\end{equation}
Then, one can check that 
\begin{equation}\label{hamiltonianCasimir}
	\mathcal{H}=\frac{1}{2}\Delta^{x,y}(C_{2})-\twoj(2\twoj+N)
\end{equation}
where $\Delta^{x,y}(C_2)$ denotes a copy of $\Delta(C_2)$ acting on  
the edge $(x,y)\in \mathcal{E}$.

@@

\begin{equation}\label{OriginalHamiltonian}
	\begin{split}
		H=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}H_{x}
	\end{split}
\end{equation}
where the edge Hamiltonian is
\begin{equation}\label{edgeHamiltonian}
\mathcal{H}_{x,y}=\sum_{a,l=1}^{N}E_{al}^{x}\otimes E_{la}^{y}-E_{ll}^{x}\otimes E_{aa}^{y}
 \end{equation}
 and where the site Hamiltonian is
 \begin{equation}\label{siteHamiltonian}
H_{x}=\sum_{a,l=1}^{N}\alpha_{a}^{x}\left(E_{al}^{x}-E_{ll}^{x}\right)
\end{equation}
Here $E_{al}^{x}$ is a copy of $E_{al}$ defined in \eqref{actionE} acting on site $x$.

We can write this Hamiltonian in function of the coproduct of the second Casimir
\begin{equation}
    C_{2}=\sum_{a,b=1}^{N}E_{ab}E_{ba}
\end{equation}
It reads
\begin{equation}
	\mathcal{H}_{x,y}=\left\{\frac{1}{2}\Delta^{xy}(C_{2})-\twoj(2\twoj+N)\frac{1}{2}\mathbbm{1}^{x}\otimes\mathbbm{1}^{y}\right\}
\end{equation}
Here we introduced the standard coproduct
\begin{equation}
\begin{split}
\Delta:gl(N)&\to gl(N)\otimes gl(N)\\
E_{ab}&\to E_{ab}\otimes \mathbbm{1}+\mathbbm{1}\otimes E_{ab}
\end{split}
\end{equation} acting on sites $x,y$ and used that $C_{2}|n\rangle=\twoj(\twoj+N)|n\rangle$. 
\end{comment}

@@

    \widetilde{H}=\sum_{x,y\in \mathcal{E}}\omega_{x,y}\mathcal{H}_{x,y}+\sum_{x\in V}\Gamma_{x}\widetilde{H}_{x}
where $\mathcal{H}_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 

@@

    \mathcal{H}_{x,y}^{T}D=D\mathcal{H}_{x,y}\qquad \forall (x,y)\in \mathcal{E}

@@

\paragraph{Proof of \eqref{edgeDualRealtion}.}To show this relation we need two 'ingredients'. First the existence of a similarity transformation between the Hamiltonian $\mathcal{H}_{x,y}$  and its transposed. As we will show, this similarity transformation is $R_{x}R_{y}$.  Second, the possibility of finding a symmetry for the edge Hamiltonian. Exploiting \eqref{hamiltonianCasimir}, we will search for a symmetry of the second Casimir $C_{2}$. As we will see, this symmetry is $\sum_{a=2}^{N}E_{a1}$ \\
We first look for the similarity between $\mathcal{H}_{x,y}$ and its transposed. Using \eqref{transpositionPropertyR} we obtain

\begin{equation}\label{transpositionPropertyH}
    \mathcal{H}_{x,y}^{T}=\left(R_{x}R_{y}\right)\mathcal{H}_{x,y}\left(R_{x}R_{y}\right)^{-1}
\end{equation}
therefore we have found the similarity transformation between $\mathcal{H}_{x,y}$ and its transposed. \\
We now look for a symmetry of $\mathcal{H}_{x,y}$, i.e. a matrix $S_{x,y}$ of the same dimension such that it satisfies 
\begin{equation}
	\mathcal{H}_{x,y}S_{x,y}=S_{s,y}\mathcal{H}_{x,y}\quad \Leftrightarrow \quad [\mathcal{H}_{x,y},S_{x,y}]=0
\end{equation}
Using \eqref{hamiltonianCasimir}, we observe that $\mathcal{H}_{x,y}$ is proportional to the coproduct of the second Casimir, up to a diagonal term. Therefore, it is enough to look for a symmetry of $\Delta (C_{2})$. Using the bilinearity of the coproduct operator and the fact that $C_{2}$ belongs to the centre of the Lie algebra, it is easy to show that for any matrix $E\in gl(N)$ it holds
\begin{equation}
	[C_{2},E]=0\quad \Rightarrow\quad \left[\Delta (C_{2}),\Delta(E)) \right]=0
\end{equation}
We chose 
\begin{equation}
	E=\sum_{a=2}^{N}E_{a1}
\end{equation}
and, for a fixed $(x,y)\in \mathcal{E}$, we define
\begin{equation}
	S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. Therefore, this operator $S_{x,y}$ satisfies
\begin{equation}\label{symmetryH}
	\left[S_{x,y},\mathcal{H}_{x,y}\right]=0
\end{equation}
i.e. it is a symmetry of $\mathcal{H}_{x,y}$. \\ Exploiting these considerations we write

\begin{comment}
As already pointed out, $\mathcal{H}_{x,y}$ is a linear function of $\Delta(C_{2})$. This implies that symmetries of  $\Delta(C_{2})$ are also symmetries of  $\mathcal{H}_{x,y}$. Moreover, the coproduct is a Lie algebra homomorphism, i.e. $\forall A,B\in gl(N)$
\begin{equation}\label{symmetryCoproduct}
    [A,B]=0\quad \Longrightarrow\quad \left[\Delta(A),\Delta(B)\right]=0
\end{equation}
This tells us that it is enough to find a symmetry of $C_{2}$. This element belongs to the center of $gl(N)$, and therefore it commutes with all the element of this algebra. Consider
\begin{equation}\label{equationE}
    E=\sum_{a=2}^{N}E_{a1}
\end{equation}
To obtain a product structure of the elements of the duality matrix, we introduce
\begin{equation}
    S=\exp{(\Delta(E))}
\end{equation}
Finally, for fixed $(x,y)\in \mathcal{E}$, we define
\begin{equation}
    S_{x,y}=\exp{(\Delta^{x,y}(E))}=\exp{(E^{x})}\exp{(E^{y})}
\end{equation}
where $\Delta^{x,y}(E)$ is a copy of the coproduct acting on sites $x$ and $y$. This operator $S^{x,y}$ satisfies
\begin{equation}\label{symmetryH}
    \left[S_{x,y},\mathcal{H}_{x,y}\right]=0
\end{equation}
i.e. $S_{x,y}$ is a symmetry of $\mathcal{H}_{x,y}$. \\ Exploiting these considerations we write
\end{comment}
\begin{equation}
    \begin{split}
        \mathcal{H}_{x,y}^{T}D&=(R_{x}R_{y})\mathcal{H}_{x,y}(R_{x}R_{y})^{-1}\left(d_{x}\otimes\dd\right)\left(d_{y}\otimes\mathcal{D}_{\widehat{y}}\right)\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=\left(R_{x}\exp{(E^{x})}\otimes \dd\right)\left(R_{y}\exp{(E^{y})}\otimes \mathcal{D}_{\widehat{y}}\right)\mathcal{H}_{x,y}\prod_{z\in V\,:\, z\neq x,y}\left(d_{z}\otimes \mathcal{D}_{\widehat{z}}\right)
        \\&=
        D\mathcal{H}_{x,y}
    \end{split}
\end{equation}
 where we used \eqref{transpositionPropertyH} and \eqref{symmetryH} in the second equality. Thus, \eqref{edgeDualRealtion} is proved. 
 %\textbf{Reamrk}: it is important to notice that the elements of the duality matrix \eqref{dualityElements} are well defined only if at each site $x\in V$ and for every species $a\in \{2,\ldots,N\}$ the number of dual particles $r_{x}^{a}$ is lower or equal than the number of original particles $n_{a}^{x}$. This implies that the dynamics of the dual process is simpler, because described by a lower number of particles. By the way, it is possible to perform computations similar to the one made in this proof choosing instead of  \eqref{equationE} {\color{red} $E=\sum_{a=2}^{N}E_{1a}$ or $E=\sum_{a=2}^{N}E_{aa}$.}
 %{\color{blue} That's confusing. What is E?}

@@

in short
\begin{equation}\label{HadTransfBoundary}
\exp{(-E^{x})}\sum_{a=1}^{N}\sum_{b=1}^{N}\alpha_{a}^{x}\left(E_{b a}^{x}-E_{bb}^{x}\right)\exp{(E^{x})}=	\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{a=2}^{N}\left(\rho_{a}^{x}E_{1a}^{x}-E_{aa}^{x}\right)

@@

	H=H_{1}+H_{bulk}+H_{L}

@@

	H_{1}=\begin{pmatrix}

@@

	H_{L}=\begin{pmatrix}

@@

reduces to the identity which implies 
\begin{equation}\label{transpostionPropertyFund}
e_{ab}^T= e_{ba}
 Therefore, the duality matrix reads

@@

	\widetilde{H}=\widetilde{H}_{1}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{L}

@@

Without loss of generality, we further assume that $\langle W|V\rangle=1$. 
\newline \newline

@@

	H\;\xrightarrow{S_{1}}\;H^{'}\;\xrightarrow{S_{2}}\;H^{''}
where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Thanks to these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} of the operators $(X_{a})_{a\in\{1,\ldots,N\}}$ of the MPA become simpler, therefore, the right eigenvector with vanishing eigenvalue $|\Psi^{''}\rangle$ of $H^{''}$ will be written explicitly. Then, reversing the transformations we will retrieve $|\Psi\rangle$.

The first transformation $S_{1}$ is closely related to the dual matrix. Moreover, we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $S_{2}$ diagonalize the right boundary. The composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra, paying the price of having left boundary that depends on the difference between the densities of the two reservoirs.

The computation are organized as follows: we first define the similarity transformations $S_{1},S_{2}$ and the Hamiltonians $H^{'},H^{''}$. Second, we compute right eigenvector with vanishing eigenvalue of $H^{''}$ thanks to the simpler commutators. Finally, we invert the similarities and retrieve the right eigenvector with vanishing eigenvalue of $H^{'}$ and the steady state of $H$.
{\color{blue}We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA gives the steady state in terms of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bula} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat2017exact}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state  $|\Psi\rangle$ using only the \eqref{bula}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \ref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relations simpler, and allows to find the steady state $|\widetilde\Psi\rangle$ of a transformed Hamiltonian, denoted  $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section~\ref{sectionDuality}. Indeed, the similarity transformation $\mathcal{S}$ relies on an "intermediate transformation" $V$ (see \eqref{transformationV}) that is, up to the diagonal operator $R$, the duality matrix.} \com{clarify}
\subsubsection{The similarity transformations}\label{subsectionSTransf}
Consider the matrices
	\mathcal{S}_{1}:=\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}\label{S1Gen}\\
	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}\right)}\label{S2Gen}
We introduce the first transformation as
\begin{equation}\label{transformationV}
 \mathcal{S}_{1}^{x}:=\exp{\left(\sum_{a=2}^{N}e_{1a}^{x}\right)}%=\mathbbm{1}+\sum_{a=2}^{N}e_{1a}
that is composed by a copy of $\mathcal{S}_{1}$ acting at site $x$ and with identities acting at all other sites of the chain. 
Observe that $\mathcal{S}_{1}^{x}$ is the transposed of the bulk part of the duality matrix $d_{x}$  at site $x\in \{1,\ldots,L\}$ (see \eqref{bulkElementDualityMatrix}). By taking the product over the chain we define
    S_{1}=\prod_{x=1}^{L}\mathcal{S}_{1}^{x}
that is related with the duality matrix by 
S_{1}=\prod_{x=1}^{L}d_{x}^{T}
 This $S_{1}$ is invertible, then we introduce 
\begin{equation}\label{hatHamiltonian}
   H^{'}:=H^{'}_{1}+H_{bulk}+H^{'}_{L}
that is related to $H$ by
\begin{equation}\label{similarV}
   H^{'}=S_{1}H^{'}S_{1}^{-1}
The bulk part of the Hamiltonian is left unchanged while the boundaries are given by 
	H^{'}_{1}=\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)\qquad H^{'}_{L}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
Indeed, using \eqref{HadTransfBoundary}, \eqref{ratesConditions} and \eqref{transpostionPropertyFund}, we obtain for the left boundary
		H_{1}^{'}&=S_{1}H_{1}S_{1}^{-1}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}
		\left\{\exp{\left(-\sum_{c=2}^{N}e_{c1}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ba}^{1}-e_{bb}^{1}\right)\exp{\left(\sum_{c=2}^{N}e_{c1}^{1}\right)}\right\}^{T}
		\sum_{a=2}^{N}\left(\alpha_{a}e_{1a}^{1}-e_{aa}^{1}\right)^{T}
		\sum_{a=2}^{N}\left(\alpha_{a}e_{a1}^{1}-e_{aa}^{1}\right)
Similarly, for the right boundary we have 
H_{1}^{'}=\exp{\left(\sum_{c=2}^{N}e_{1c}^{1}\right)}\sum_{a,b=1}^{N}\alpha_{a}\left(e_{ab}^{1}-e_{bb}^{1}\right)\exp{\left(-\sum_{c=2}^{N}e_{1c}^{1}\right)}=\sum_{a=2}^{N}\left(\beta_{a}e_{a1}^{L}-e_{aa}^{L}\right)
